\textsf{Are large language models superhuman chemists?}

### 2024-10-28 src/tex/appendix.tex
Update appendix.tex

Larger models generally perform better (\LlamaThreeOneFourZeroFiveBInstruct > \LlamaThreeOneSeventyBInstruct > \LlamaThreeOneEightBInstruct). However, smaller but well-designed models can compete with larger models. For example, \GemmaTwoNineBIt has an overall accuracy of 0.48 on \ChemBench corpus, which is only 10\% less accurate than the much larger \LlamaThreeOneFourZeroFiveBInstruct model.
One can observe a clear progression of performance across model families (e.g., \ClaudeThreeFiveSonnet >  \ClaudeThree > \ClaudeTwo). Newer versions consistently outperform their predecessors, indicating improvements in scientific understanding of these model families.
Scores of knowledge-intensive are generally lower than those of Calculation and Reasoning. Reasoning tends to be the strongest skill among the three.

>>>>

Larger models generally perform better (\LlamaThreeOneFourZeroFiveBInstruct > \LlamaThreeOneSeventyBInstruct > \LlamaThreeOneEightBInstruct). However, smaller but well-designed models can compete with larger models. For example, \GemmaTwoNineBIt has an overall accuracy of 0.48 on \ChemBench corpus, which is only 10\% less accurate than the much larger \LlamaThreeOneFourZeroFiveBInstruct model.
One can observe a clear progression of performance across model families (e.g., \ClaudeThreeFiveSonnet >  \ClaudeThree > \ClaudeTwo or \GPTFourO > \GPTFour > \GPTThreeFiveTurboZeroT). Newer versions consistently outperform their predecessors, indicating improvements in scientific understanding of these model families.
Scores of knowledge-intensive are generally lower than those of Calculation and Reasoning. Reasoning tends to be the strongest skill among the three.
